Comparing Models of Delta-Notch Signalling

### 2025-04-11 paper/paper.tex
Capitalise delta in Table1; rewrite key assumptions in Appendix C

\subsection*{Key Assumptions}
Throughout this derivation, we make the following assumptions:
\begin{enumerate}
  \item Fluctuations in molecular counts are small relative to their mean values; that is, $\sqrt{\text{Var}(N)} \ll \langle n \rangle$, $\sqrt{\text{Var}(D)} \ll \langle d \rangle$, and $\sqrt{\text{Var}(I)} \ll \langle i \rangle$.

  \item Second moments can be approximated by the squares of the means, i.e., $\langle n^2 \rangle \approx \langle n \rangle^2$, $\langle d^2 \rangle \approx \langle d \rangle^2$, and $\langle i^2 \rangle \approx \langle i \rangle^2$.

  \item Molecular species are approximately uncorrelated, so that joint moments factorize, e.g., $\langle n \cdot d \rangle \approx \langle n \rangle \langle d \rangle$.

>>>>

\subsection*{Key Assumptions}
Throughout this derivation, we make the following assumptions:
\begin{enumerate}
  \item The standard deviation of molecular counts is small compared to their mean values, $\sqrt{\text{Var}(N)} \ll \langle n \rangle$, $\sqrt{\text{Var}(D)} \ll \langle d \rangle$, and $\sqrt{\text{Var}(I)} \ll \langle i \rangle$.

  \item The second moments can be approximated by the squares of the means, i.e., $\langle n^2 \rangle \approx \langle n \rangle^2$, $\langle d^2 \rangle \approx \langle d \rangle^2$, and $\langle i^2 \rangle \approx \langle i \rangle^2$.

  \item Molecular counts are approximately independent, so that joint moments factorize, e.g., $\langle n \cdot d \rangle \approx \langle n \rangle \langle d \rangle$.
